Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-28 writing/CONUS_AOD.qmd
Show the name of the center state in `pred.map.median.mse`.

```{r pred.map.median.mse}
#| label: fig-map-median-mse
#| fig-cap: Maps of typical MAIAC and Corrected AOD. Day selected as having the median improvement in MSE at AERONET sites.
IG(tar_read(pred.map.median.mse.path))
```

>>>>

```{r pred.map.median.mse}
#| label: fig-map-median-mse
#| fig-cap: !expr caption
caption = sprintf("Maps of typical MAIAC and Corrected AOD. Day selected as having the median improvement in MSE at AERONET sites. The map is centered on %s.",
    tar_read(median.mse.map)$center.name)
IG(tar_read(pred.map.median.mse.path))
```
